---
title: "STA 141B HW3"
author: "Howie Huang"
date: "5/23/2022"
output: pdf_document
---

```{r,results='hide',warning=FALSE,message=FALSE,echo=FALSE}
library(DBI)
library(RSQLite)
library(tidyverse)

db<- dbConnect(SQLite(), "~/Desktop/StatsSO.sqlite")
```

***
#1 What is the date range for the questions and answers in this database?
```{r,results='hide',warning=FALSE,message=FALSE,}
date.question<-dbGetQuery(db,'SELECT CreationDate 
                   FROM Posts 
                   WHERE PostTypeId ="1"
                   AND CreationDate != "NA"
                   ORDER BY CreationDate ASC')

date.answer<-dbGetQuery(db,'SELECT CreationDate 
                   FROM Posts 
                   WHERE PostTypeId ="2"
                   AND CreationDate != "NA"
                   ORDER BY CreationDate ASC')
range.date.question<-c(date.question[1,],date.question[nrow(date.question),]) %>% print
range.date.answer<-c(date.answer[1,],date.answer[nrow(date.answer),]) %>% print
rm(date.question,date.answer)
```

***
#2 How many users are there?
```{r,results='hide',warning=FALSE,message=FALSE,}
num.user<-as.integer(dbGetQuery(db,'SELECT COUNT(Id) 
                                FROM Users')) %>% print
rm(num.user)
```

***
#3 How many users joined since 2020?
```{r,results='hide',warning=FALSE,message=FALSE,}
num.2020<-nrow(dbGetQuery(db,'SELECT CreationDate 
                          FROM Users 
                          WHERE CreationDate > "2020%"')) %>% print 
rm(num.2020)
```

***
#4 How many users joined each year? Describe this with a plot.
```{r,results='hide',warning=FALSE,message=FALSE,}
num.user.2009<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2009"')
num.user.2010<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2010"')
num.user.2011<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2011"')
num.user.2012<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2012"')
num.user.2013<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2013"')
num.user.2014<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2014"')
num.user.2015<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2015"')
num.user.2016<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2016"')
num.user.2017<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2017"')
num.user.2018<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2018"')
num.user.2019<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2019"')
num.user.2020<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2020"')
num.user.2021<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2021"')
num.user.2022<-dbGetQuery(db,'SELECT COUNT(*) 
                          FROM Users 
                          WHERE strftime("%Y", CreationDate) = "2022"')
num.user.eachyear<-as.integer(c(num.user.2009,num.user.2010,num.user.2011,num.user.2012,num.user.2013,num.user.2014,
                              num.user.2015,num.user.2016,num.user.2017,num.user.2018,num.user.2019,
                              num.user.2020,num.user.2021,num.user.2022)) %>% print

year<-c(2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022)
df<-data.frame(year,num.user.eachyear)
plot(num.user.eachyear~year, data=df)

rm(num.user.2009,num.user.2010,num.user.2011,num.user.2012,num.user.2013,num.user.2014,
   num.user.2015,num.user.2016,num.user.2017,num.user.2018,num.user.2019,
   num.user.2020,num.user.2021,num.user.2022,df,year)
```

***
#5 How many users have asked at least one question?
```{r,results='hide',warning=FALSE,message=FALSE,}
num.user.1q<-as.integer(dbGetQuery(db,'SELECT COUNT(DISTINCT(OwnerUserId)) 
                     FROM Posts
                     WHERE PostTypeId ="1"'))%>% print

    # How many have only answered questions?
num.user.ansonly<-as.integer(dbGetQuery(db,'SELECT COUNT(DISTINCT(OwnerUserId))
                     FROM Posts
                     WHERE NOT PostTypeId IN ("1","3","4","5","6","7","8")
                     AND NOT OwnerUserId IN (SELECT DISTINCT(UserId) FROM Comments)'))

    # How many have only commented?
num.user.comonly<-as.integer(dbGetQuery(db,'SELECT COUNT(DISTINCT(UserID))
                     FROM Comments
                     WHERE NOT UserId IN (SELECT DISTINCT(OwnerUserId) FROM Posts)'))

    # How many have not posted anything (question, answer or comment)?
num.user.none<-as.integer(dbGetQuery(db,'SELECT COUNT(DISTINCT(Id))
                     FROM Users
                     WHERE NOT Id IN (SELECT DISTINCT(OwnerUserId) FROM Posts)
                     AND NOT Id IN (SELECT DISTINCT(UserId) FROM Comments)'))
rm(num.user.1q,num.user.ansonly,num.user.comonly,num.user.none)
```

***
#6 What user answered the most questions?
```{r,results='hide',warning=FALSE,message=FALSE,}
user.most.ans<-dbGetQuery(db,'SELECT OwnerUserId,COUNT(Id) 
                     FROM Posts
                     WHERE PostTypeId = "2"
                     GROUP BY OwnerUserId
                     ORDER BY COUNT(Id) DESC')[1,]
rm(user.most.ans)
```

***
#7 Do users with badges tend to answer more questions than they ask?
```{r,results='hide',warning=FALSE,message=FALSE,}
    # number of questions asked by users with badges 
dbGetQuery(db,'SELECT OwnerUserId,COUNT(Id) AS num_question
           FROM Posts
           WHERE PostTypeId = "1"
           AND OwnerUserId IN 
           (SELECT UserId
           FROM Badges)
           GROUP BY OwnerUserId
           ORDER BY COUNT(Id) DESC')
    # number of answers made by users with badges
dbGetQuery(db,'SELECT OwnerUserId,COUNT(Id) AS num_answer
           FROM Posts
           WHERE PostTypeId = "2"
           AND OwnerUserId IN 
           (SELECT UserId
           FROM Badges)
           GROUP BY OwnerUserId
           ORDER BY COUNT(Id) DESC')
```

***
#8 How many different types of posts are there in the Posts table?
```{r,results='hide',warning=FALSE,message=FALSE,}
post.type<-dbGetQuery(db,'SELECT DISTINCT(PostTypeId)
                     FROM Posts
                     ORDER BY PostTypeId ASC')
rm(post.type)
```

***
#9 What proportion of questions have an accepted answer and don’t?
```{r,results='hide',warning=FALSE,message=FALSE,}
qwithaa<-dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND AcceptedAnswerId != "NA"')

qwithoutaa<-dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND AcceptedAnswerId = "NA"')

num.q<-dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"')
as.numeric(qwithaa/num.q)
as.numeric(qwithoutaa/num.q)
rm(qwithaa,qwithoutaa)
```

***
#11 What’s the most recent question in the Posts table?
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT Id,CreationDate
           FROM Posts
           WHERE PostTypeId = "1" AND CreationDate != "NA"
           ORDER BY CreationDate DESC
           LIMIT (50)')[1,]
```

***
#12 What are the top 50 most common tags on questions?
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT Tags
           FROM Posts
           WHERE PostTypeId = "1"
           GROUP BY Tags
           ORDER BY COUNT(Tags) DESC
           LIMIT 50')
```

***
#13 For each of the top 50 tags on questions, how many questions are there for each tag.
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT Tags,COUNT(Tags)
           FROM Posts
           WHERE PostTypeId = "1"
           GROUP BY Tags
           ORDER BY COUNT(Tags) DESC
           LIMIT 50')
```

***
#17 How many questions are there each year?
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2009"')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2010" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2011" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2012" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2013" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2014" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2015" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2016" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2017" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2018" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2019" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2020" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2021" ')
dbGetQuery(db,'SELECT COUNT(Id)
           FROM Posts
           WHERE PostTypeId = "1"
           AND strftime("%Y", CreationDate) = "2022" ')
```

***
#16 Programmatically find the questions where there are more comments than answers?
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT Id
           FROM Posts
           WHERE PostTypeId = "1"
           AND CommentCount > AnswerCount')
```

***
#20 How many questions have the terms Regression, ANOVA, Data Mining, Machine Learning, Deep Learning, Neural Network,
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT Tags,COUNT(Tags)
           FROM Posts
           WHERE PostTypeId = "1"
           AND Tags LIKE "%regression%" or Tags LIKE "%ANOVA%"
           or Tags LIKE "%data_mining%" or Tags LIKE "%machine_learning%"
           or Tags LIKE "%deep_learning%" or Tags LIKE "%neural_network%"
           GROUP BY Tags
           ORDER BY COUNT(Tags) DESC')

dbGetQuery(db,'SELECT COUNT(Tags)
           FROM Posts
           WHERE PostTypeId = "1"
           AND Tags LIKE "%regression%" or Tags LIKE "%ANOVA%"
           or Tags LIKE "%data_mining%" or Tags LIKE "%machine_learning%"
           or Tags LIKE "%deep_learning%" or Tags LIKE "%neural_network%"')
```

***
#23 Are there users in the Posts table that are not in the Users table? If so, how many and is there any pattern to this? 
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT COUNT(OwnerUserId)
           FROM Posts
           WHERE NOT OwnerUserId IN 
           (SELECT Id 
           FROM Users)')
```

***
#29 How is the user’s reputation related to the accepted answers?
```{r,results='hide',warning=FALSE,message=FALSE,}
dbGetQuery(db,'SELECT Users.Id,Users.Reputation, COUNT(Posts.Id) AS Count_acceptedAnswer 
           FROM Users
           LEFT JOIN Posts
           ON Posts.OwnerUserId = Users.Id
           WHERE Users.Id != "-1"
           GROUP BY Users.Id
           ORDER BY Users.Reputation DESC
           LIMIT (100)')

dbGetQuery(db,'SELECT Users.Id,Users.Reputation, COUNT(Posts.Id) AS Count_accpetedAnswer 
           FROM Users
           LEFT JOIN Posts
           ON Posts.OwnerUserId = Users.Id
           WHERE Users.Id != "-1"
           GROUP BY Users.Id
           ORDER BY Users.Reputation ASC
           LIMIT (100)')
```

***
#30 Do the people who vote tend to have badges?
```{r,results='hide',warning=FALSE,message=FALSE,}
    # number of votes for each person
num.vote<-dbGetQuery(db,'SELECT UserId,COUNT(Id)
           FROM Votes
           WHERE UserId != "NA"
           AND UserId != "-1"
           GROUP BY UserId
           ORDER BY COUNT(Id) DESC')

    # number of badges for each person
num.badge<-dbGetQuery(db,'SELECT UserId,COUNT(Id)
           FROM Badges
           WHERE UserId != "NA"
           AND UserId != "-1"
           GROUP BY UserId
           ORDER BY COUNT(Id) DESC')
```